\documentclass[12pt]{article}

\usepackage{cite}

\title{Vista Map}

\author{Jordan Clark and Nickoli Londura \\
       ONID: clarkj3 and londuran    }



\begin{document}

\maketitle

In our world there are lots of problems that people encounter, and there is a need for solutions that will make life easier. Software can provide solutions to many of these problems. Vista points are places where people can stop and look at the scenery and relax before going back on the road. Unfortunately, these vista points are poorly marked. Some maps mark out the location of these vista points, however, they are not reliable resources. According to California Department of Transportation, they only show approximate locations in California where vista points can be found but not specifically where \cite{california_department_of_transportation_2015}. Often, when driving on the freeway, people will see a sign to a vista point less than a mile away but they are too many lanes over on the freeway to make the exit in time and so they miss it. Signs without much warning and maps with unreliable information make it hard for people to actually get to a vista point. Software could be used to let people know where the vista points are and so that people know where to find them and don’t miss the exit to go see them.

There is a problem that is being faced right now where people are having a hard time finding vista points as they travel. There are websites that barely talk about where vista points are located at, as well as only showing partial places that people can go see. People are always having trouble finding vista points near the places they are traveling to. This happens either by not being able to find signs that point in the right direction, or seeing them too late because they would be in the far lane of the freeway. People haven’t really put much effort into creating a way for others to be able to find vista points quicker and with ease. People are always trying to look for vista points but come up with barely any info regarding their locations. According to California Department of Transportation, they only have a minimal amount of info on vista points, like what they provide for the public but not where to find them \cite{california_department_of_transportation_2018}. There are other websites that give a few amount of vista point locations. According to “Scenic Viewpoints \& Turnouts,” they have a brief list of places that people can find and go to see scenic views \cite{scenic_viewpoints}. However, this list is limited. There is a need for a solution that would make it easier to find many vista points around the country.

People that are taking a road trip, they are going to want to stop by many places that have scenic views. Finding these types of places is very difficult because there aren’t any maps that show their positions, and while driving on unfamiliar roads it is easy to miss the signs that point to vista points. There can also be problems where people finally see a sign to go to a vista point but it usually turns out to be too late to pull off the road and would have to turn around. What most people likely do to find them is to either ask for directions or try to find signs that point or give direction to the nearest vista point. People need some type of solution in order to be able to find and get to the vista points without any problems.

A solution for finding vista points is an application that actually marks them on a map. While driving on the road, people can use an app that is specifically designed to show vista points on a map, and people would be able to see them ahead of time to know which direction they need to be going in order to find them. Based on a person’s location, the map would show all the vista points nearby, and people would be able to mark any one of them. The application would also have an option for finding vista points using a nearby city or using a zip code and provide all the vista points around that specific location. Creating an application makes the problem of finding vista points manageable because people will always be able to find a vista point nearby without any problems.

An approach for making it easier to find vista points is to create an application that uses a map, which allows people to mark vista points that they see. When someone marks the point it is automatically added to everyone’s map that also has the app. The more people that use the app, the more vista locations will be marked. Individual people that find vista points will be adding them to the app and in turn give other people a chance to find and visit those same places. There could also be an option for the app to notify people when they are approaching a vista point so that they won’t miss it. This application could either be an add-on to Google maps or have it as its own map. Using this kind of an approach for finding vista points addresses the problem very well because locations will constantly be added as users input new and different vista locations, filling the map for all users to access.

Since the time that electronic maps have been made, there has not yet been an option to find vista points anywhere in the country. The idea of creating an application by marking and finding vista points is an original. This approach will be the first for creating an application that uses a map to show many vista point locations throughout the country and people can use it to find and mark them. Others might have had ideas about creating something like this, but there isn’t any other software right now that people use which can be compared to. This will be a new idea that will utilize the current usage of maps and make them be more efficient for others to interact with.

This application would have features that will bring efficiency to people as they are using it. One feature that the app provides is using data from crowdsources to improve locations, which will allow people to have accurate information where the vista points are at. Having many user inputs for different locations will create a better usage for everyone because there will be more vista points that people can visit. Another great feature is having a notification system, where it will notify people when vista points are nearby. This is very useful because it will prevent people from missing the vista point or have difficulties finding the signs along the road. The more people put into the app the more everyone will get benefits out of it.

Looking at the application, even though it has good features and will be very beneficial, it still has limitations. This app is designed to be used by lots of people because the more people that use it, the more vista points will be shown on the map. However, if only a few number of people use it, then the app wouldn’t grow and there would be hardly any vista points for people to see making it and unreliable source for finding all vista points. Even though this app has a great feature for allowing people to mark vista points that they come across, it could be its downfall as well if there aren’t a whole lot of people using it. This feature is a potential risk but could be worthwhile if the app would grow over time.

Creating this application is going to be based mostly on the software because it is designed to run on different devices. It is important to have the software running smoothly in order for the features of the app to work properly. There could be some potential for having bugs while in the process of making it, or even after its done, but the main goal is to have the software at least run the app. There will also be a need to have a database in order to create the map that the app will be using. Having a database would mean that it will be possible to store all the different vista points that people mark, as well as having an actual map of a region, if the app has its own make and isn’t implemented as an add on to Google maps.

If implemented as an add on to Google maps, working to create the software for the application comes with a challenge to make it compatible with Google maps. Google maps have their own software that they run, and it could be troublesome to find a way for the app to be compatible with their map, as well as having Google agree to add the vista point software. There isn’t really a solution to work on beforehand because there is a limited time allowed to have the software ready. There is also a general challenge of learning the process and the skills to implement the product in time. When making new software there are no steps to follow while in process of writing the software, but only to just figure it out along the way.

How the vista point application is going to work is just run on devices that are tablets or smartphones. The app is going to be designed to just be either be an add-on to Google maps or have its own map. It wouldn’t matter what the hardware is as long as the devices are able to use a map. When using Google maps, the vista point software is going to be an option that people can choose to activate. When activated vista points will be marked on Google maps with and icon as well as a button that would allow people to add or mark new vista points.  If the app is implemented as its own users will see a map that has all vista points marked. Selecting a vista point would give the user the specific address of that point so that they can easily find it. Additional users will be given the ability to add new vista points to the map. With this application, people will have an easier time finding vista points and growing the app will allow all the vista points to be on the map.



\bibliography{myref}

\bibliographystyle{plain}



\end{document}